Crossing Origins by Crossing Formats

### 2012-11-30 main.tex
update

@@

\subsection{Syntax injection}
the minimal malformed structure that is required for Adobe Reader to consider ita PDF.

>>>>

\todo{discuss the layout}

\subsection{Infiltrating the origin}

A form of injection attack.

\subsubsection{Polyglot upload}

A form of content repurposing attack.

\subsection{Scenarios}

After infiltrating an origin two lines of exploitation is available.

\subsubsection{Cross-domain leakage}

Extract sensitive information and send to attacker

\subsubsection{Cross-site request forgery}

Extract CSRF protection token and do CSRF attack, despite protection!

@@

Based on the minimal PDF sample in Listing~\ref{lst:minimal-pdf}, we can derive 
the set of tokens required to build a PDF. Assuming that alpha-numeric characters pass through any filter unmodified, this set is ${\%, <<, >>, (, ), /}$.
